Dirac neutrino mass generation from Majorana messenger

### 2019-09-15 draft.tex
lc

\section{Collider constraints}
The recasting of the latest ATLAS results for the search of dilepton resonances using $139\ \text{fb}^{-1}$~\cite{Aad:2019fac} was done
in~\cite{Chiang:2019ajm} for the $\operatorname{U}(1)_{B-L}$ model.
The green (upper) region in Fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$ To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g_{BL}$. In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{Heeck:2014zfa}, 
\begin{align}
  M_{Z'}/g_{BL}>6.7\ \text{TeV}\,,&&\text{at $95\%$ C.L }\,,
\end{align}
which is obtained from the search for effective four-lepton operators and valid for $M_{Z'}\gg 200\ \text{GeV}$. This constraint is relevant for $M_{Z'}>5.8\ \text{TeV}$, and is shown in the excluded magenta (lower) region of Fig.~\ref{fig:u1blc}.

>>>>

\section{Collider constraints}
The recasting of the latest ATLAS results for the search of dilepton resonances using $139\ \text{fb}^{-1}$~\cite{Aad:2019fac} was done
in~\cite{Chiang:2019ajm} for the $\operatorname{U}(1)_{B-L}$ model.
The green (upper) region in fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$ To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g_{BL}$. In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{Heeck:2014zfa}, 
\begin{align}
  M_{Z'}/g_{BL}>6.7\ \text{TeV}\,,&&\text{at $95\%$ C.L }\,,
\end{align}
which is obtained from the search for effective four-lepton operators and is valid for $M_{Z'}\gg 200\ \text{GeV}$. This constraint is relevant for $M_{Z'}>5.8\ \text{TeV}$, and corresponds to the excluded magenta (lower) region of fig.~\ref{fig:u1blc}.
